### 2017-02-27 paper/chapters/introduction.tex
removed quote
added caption2img example, further applications (todo)

"What I cannot create, I do not understand." -- Richard Feynman \\\\

Directed generative models are a wide class of models used for generating samples from an unknown distribution $p_{data}$.
%Lets denote $p_{data}$ as the unknown real-world data distribution from which samples in the given dataset are drawn.
The presented models in this article will approximate $p_{data}$ with $p_{model}$ which enables us to draw samples from the model.
Under the assumption that $p_{model}$ approximates $p_{data}$ accurately, samples from the true data distribution should have high likelihood under the approximation as well.\\\\

>>>>

\begin{figure}[h]
  \includegraphics[width=\linewidth]{media/caption2img}
  \caption[Caption to Image]{Images generated given a captioning text \cite{gan_t2i:2016}}
  \label{fig:caption2img}
\end{figure}
While sampling from generative models has by itself interesting applications, such as producing images given a caption as seen in Figure \ref{fig:caption2img}, there are many applications covering various different areas.
A subset of these applications include
image denoising, % TODO: citation
image impainting, % TODO: citation
text-to-speech, % TODO: citation, e.g. WaveNet
machine translation, % (neural?) TODO: e.g. NMT w/ VAE
and semi-supervised learning, for example discussed in \ref{ssub:cvae}.
\\\\

%Directed generative models are a wide class of models used for generating samples from an unknown distribution $p_\mathrm{data}$.
%The models presented in this article will approximate $p_\mathrm{data}$ with $p_\mathrm{model}$ which enables us to draw samples from the model.
%Given this assumption, samples from a dataset following $p_\mathrm{data}$ should have high likelihood in $p_\mathrm{model}$ too.\\\\

Generative models are in particular interesting as they
